Confirmation of \srcfull{} as a long period radio transient

### 2025-05-22 paper/main.tex
Latest synch of paper with Overleaf version.

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[S. J. McSweeney et al.]{
Samuel J. McSweeney$^{1}$,
Natasha Hurley-Walker$^{1}$,
Akash Anumarlapudi$^{2,3}$,
Dougal Dobie$^{2,3}$,
Cs\'{a}nad Horv\'{a}th$^{1}$,
\newauthor
Angie Waszewski$^{1}$,
John Morgan$^{1}$,
and Ziteng Wang$^{1}$
\\
% List of institutions
$^{1}$International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia\\
$^{2}$Sydney Institute for Astronomy, School of Physics, The University of Sydney, NSW 2006, Australia\\
$^{3}$ARC Centre of Excellence for Gravitational Wave Discovery (OzGrav), Hawthorn, VIC 3122, Australia
}

@@

%\begin{deluxetable*}{cccccc}
%\tablecaption{Pulse detections and non-detections}
%\tablehead{
%\colhead{Obs start} & \colhead{Duration} & \colhead{Telescope} & \colhead{$\nu$} & %\colhead{$\Delta\nu$} & \colhead{Detected?} \\ 
%\colhead{time (UTC)} & \colhead{(s)} & & \colhead{(MHz)} & \colhead{(MHz)} &
%} 
%\startdata
%2024-09-19 09:25:02 & 592\tablenotemark{a} & MWA & 184.96 & 30.72 & Y \\ % 1410773120 and 1410773416
%2024-09-19 10:34:06 & 592\tablenotemark{a} & MWA & 184.96 & 30.72 & Y \\ % 1410777264 and 1410777560
%2024-09-19 12:57:10 & 296 & MWA & 184.96 & 30.72 & Y \\ % 1410785848
%2024-09-19 14:06:14 & 296 & MWA & 184.96 & 30.72 & Y \\ % 1410789992
%2024-10-09 10:55:50 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1412506568
%2024-10-09 12:05:34 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1412510752
%2024-10-10 11:21:10 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1412594488
%2024-10-10 12:30:54 & 296 & MWA\tablenotemark{b} & 200.32 & 30.72 & Y \\ % 1412598672
%2024-10-11 10:36:46 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1412678224
%2024-10-11 11:46:30 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1412682408
%2024-10-12 11:02:06 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1412766144
%2024-10-12 12:11:50 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1412770328
%2024-10-13 10:17:42 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1412849880
%2024-10-13 11:27:26 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1412854064
%2024-10-14 10:43:02 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1412937800
%2024-10-14 11:52:46 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1412941984
%2024-10-16 10:23:58 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1413109456
%2024-10-16 11:33:42 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1413113640
%2024-10-17 11:59:02 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1413201560
%2024-10-19 10:30:14 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1413369032
%2024-10-19 11:39:58 & 296 & MWA & 200.32 & 30.72 & Y \\ % 1413373216
%2024-10-19 13:54:36 & 601 & MeerKAT\tablenotemark{c} & 812.8 & 247.6 & Y \\ % 1413381294
%\enddata
%\tablenotetext{a}{Two contiguous 296-second MWA observations were combined}
%\tablenotetext{b}{Too much RFI to use in downstream analysis}
%\tablenotetext{c}{Two components in pulse}
%\end{deluxetable*}

@@

%\begin{deluxetable*}{ccccc}
%  \tablecaption{Times of arrival and pulse properties\label{tbl:toas}}
%  \tablehead{
%    \colhead{Telescope} & \colhead{$\nu$} & \colhead{ToA} & \colhead{Fluence} & \colhead{$\sigma$} \\ 
%    & \colhead{(MHz)} & \colhead{(MJD)} & \colhead{(Jy\,s)} & \colhead{(s)}
%  } 
%  \startdata
%ASKAP & 888 & 59965.0429346(42) & 6.7(1) & 29.1(4) \\
%MWA & 170 & 59966.061584(40) & 358(55) & 40(7) \\
%ASKAP & 888 & 60040.913447(32) & 0.48(5) & 25(3) \\
%MeerKAT & 1284 & 60092.8995476(100) & 0.104(7) & 12.8(9) \\
%MeerKAT & 1284 & 60092.947966(10) & 0.10(1) & 12(1) \\
%MeerKAT & 1284 & 60092.996466(11) & 0.125(7) & 15.8(9) \\
%MeerKAT & 1284 & 60093.044919(12) & 0.122(7) & 16(1) \\
%MWA & 200 & 60481.637466(65) & 50(11) & 24(8) \\
%MWA & 200 & 60485.658977(33) & 29(3) & 16(4) \\
%MWA & 200 & 60489.632266(20) & 48(3) & 14(2) \\
%MWA & 200 & 60492.588020(24) & 87(7) & 14(3) \\
%MWA & 200 & 60496.609639(18) & 67(4) & 17(2) \\
%MWA & 200 & 60503.587085(14) & 82(3) & 17(2) \\
%ASKAP & 888 & 60503.6347610(51) & 3.10(8) & 16.4(5) \\
%MWA & 200 & 60506.542809(33) & 57(7) & 9(4) \\
%MWA & 200 & 60510.564531(11) & 79(3) & 16(1) \\
%MWA & 200 & 60519.528812(29) & 86(10) & 14(4) \\
%MWA & 200 & 60522.533028(16) & 76(3) & 18(2) \\
%MWA & 200 & 60527.524033(14) & 73(3) & 16(2) \\
%MWA & 200 & 60530.528339(16) & 68(4) & 17(2) \\
%MWA & 200 & 60537.506042(13) & 92(4) & 17(2) \\
%MWA & 200 & 60541.479448(47) & 41(6) & 14(5) \\
%MWA & 200 & 60544.483761(15) & 79(3) & 20(2) \\
%MWA & 200 & 60551.461625(16) & 85(4) & 16(2) \\
%MWA & 185 & 60572.395455(15) & 74(3) & 15(2) \\
%MWA & 185 & 60572.443943(21) & 73(4) & 16(2) \\
%MWA & 185 & 60572.540824(18) & 64(4) & 16(2) \\
%MWA & 185 & 60572.589281(31) & 82(8) & 21(4) \\
%MWA & 200 & 60592.456765(27) & 34(3) & 19(3) \\
%MWA & 200 & 60592.505159(33) & 35(4) & 19(4) \\
%MWA & 200 & 60593.474369(26) & 29(3) & 15(3) \\
%MWA & 200 & 60593.522901(46) & 27(4) & 19(5) \\
%MWA & 200 & 60594.443484(21) & 43(3) & 18(2) \\
%MWA & 200 & 60594.491990(33) & 19(2) & 12(4) \\
%MWA & 200 & 60595.461118(29) & 33(3) & 19(3) \\
%MWA & 200 & 60595.509617(25) & 27(2) & 13(3) \\
%MWA & 200 & 60596.430283(20) & 39(3) & 16(2) \\
%MWA & 200 & 60596.478721(23) & 39(3) & 17(3) \\
%MWA & 200 & 60597.447846(41) & 22(3) & 16(5) \\
%MWA & 200 & 60597.496319(30) & 38(4) & 19(3) \\
%MWA & 200 & 60599.434635(17) & 39(2) & 13(2) \\
%MWA & 200 & 60599.483122(24) & 32(3) & 13(3) \\
%MWA & 200 & 60600.500655(31) & 30(3) & 16(4) \\
%MWA & 200 & 60602.438964(32) & 36(4) & 21(4) \\
%MWA & 200 & 60602.487394(27) & 39(3) & 20(3) \\
%MeerKAT & 813 & 60602.5835733(40) & 1.64(4) & 14.9(4) \\
  %\enddata
%\end{deluxetable*}

@@

\begin{table}
  \centering
  \caption{Timing ephemeris for \src{}}
  \label{tbl:ephemeris}
  \begin{tabular}{lc}
    \hline
    Parameter & Value \\
    \hline
    Period (s) & $4186.3283 \pm 0.0003$ \\
    PEPOCH (MJD) & $59965.03790 \pm 0.00003$ \\
    DM (pc/cm$^{-3}$) & $764 \pm 25$ \\
    $\tau_{\rm sc,1 GHz}$ (s) & ${\sim}0.07$ \\
    \hline
  \end{tabular}
\end{table}

\begin{figure*}
  \centering
  \includegraphics[width=0.98\linewidth]{pulse_details.pdf}
  \caption{Timing residuals (top panel) and other pulse properties derived from the fits of \Eqn~\ref{eqn:emg} to the individual light curves (lower three panels). Notable features of interest include the relative high fluence of the early 2023 detections (leftmost two points), and the relative stability of the pulse fluences (and pulse morphology) of the MWA detections in the time range $60480 \le {\rm MJD} \le 60580$.}
  \label{fig:pulse_details}
\end{figure*}

The variability of the pulse brightness, coupled with the fact that none of our detections were simultaneous at multiple telescopes, prohibit a direct spectral index measurement.
We note, however, that the fitted peak flux densities of the ASKAP and MeerKAT pulses are broadly consistent with the MWA flux densities if an approximate spectral index of $-2.0$ is assumed.
The in-band spectral index measurement of $-3.1$ reported for the 2023 ASKAP pulse \citepalias{2024MNRAS.535..909D}, if consistent across the span of our observations, implies a turnover or spectral curvature at intermediate frequencies \citep[perhaps comparable with GPM\,1839$-$10][]{2023Natur.619..487H}.

The measured DM of $764 \pm 25\,{\rm pc}\,{\rm cm}^{-3}$ is slightly higher than, but still consistent with, the in-band measurement of $710^{+200}_{-180}\,{\rm pc}\,{\rm cm}^{-3}$ given in \citetalias{2024MNRAS.535..909D}.
Because we have not attempted to simultaneously fit for both DM and scattering timescale, there will remain some small systematic error on this reported DM measurement.
Note, in particular, that the YMW16 and NE2001 models predict a slightly longer scattering time scale than the $70\,$ms that we have assumed throughout this work.
Breaking the degeneracy is possible in principle with a higher S/N average profile than what is achievable with the current data set.

@@

No significant polarised emission was detected in the MWA pulses, as well as the 2023 MeerKAT pulses.
The apparent lack of polarisation in the 2023 MeerKAT data set is likely due to low S/N coupled with the source not being not being centred in the beam.
Much more careful imaging analysis would be needed to obtain reliable measurements or limits on the polarised components of those pulses.

@@

>>>>

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[S. J. McSweeney et al.]{
Samuel J. McSweeney$^{1}$,
Natasha Hurley-Walker$^{1}$,
Cs\'{a}nad Horv\'{a}th$^{1}$,
Akash Anumarlapudi$^{2,3}$,
\newauthor
Angie Waszewski$^{1}$,
Dougal Dobie$^{2,3}$,
John Morgan$^{1}$,
David Kaplan$^{?}$,
and Ziteng Wang$^{1}$
\\
% List of institutions
$^{1}$International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia\\
$^{2}$Sydney Institute for Astronomy, School of Physics, The University of Sydney, NSW 2006, Australia\\
$^{3}$ARC Centre of Excellence for Gravitational Wave Discovery (OzGrav), Hawthorn, VIC 3122, Australia
}

@@

@@

%\begin{deluxetable*}{ccccc}
%  \tablecaption{Times of arrival and pulse properties\label{tbl:toas}}
%  \tablehead{
%    \colhead{Telescope} & \colhead{$\nu$} & \colhead{ToA} & \colhead{Fluence} & \colhead{$\sigma$} \\ 
%    & \colhead{(MHz)} & \colhead{(MJD)} & \colhead{(Jy\,s)} & \colhead{(s)}
%  } 
%  \startdata
%ASKAP & 888 & 59965.0429346(42) & 13.4(2) & 29.1(4) \\
%MWA & 170 & 59966.061584(40) & 358(55) & 40(7) \\
%ASKAP & 888 & 60040.913447(32) & 1.0(1) & 25(3) \\
%MeerKAT & 1284 & 60092.8995476(100) & 0.104(7) & 12.8(9) \\
%MeerKAT & 1284 & 60092.947966(10) & 0.10(1) & 12(1) \\
%MeerKAT & 1284 & 60092.996466(11) & 0.125(7) & 15.8(9) \\
%MeerKAT & 1284 & 60093.044919(12) & 0.122(7) & 16(1) \\
%MWA & 200 & 60481.637466(65) & 50(11) & 24(8) \\
%MWA & 200 & 60485.658977(33) & 29(3) & 16(4) \\
%MWA & 200 & 60489.632266(20) & 48(3) & 14(2) \\
%MWA & 200 & 60492.588020(24) & 87(7) & 14(3) \\
%MWA & 200 & 60496.609639(18) & 67(4) & 17(2) \\
%MWA & 200 & 60503.587085(14) & 82(3) & 17(2) \\
%ASKAP & 888 & 60503.6347610(51) & 6.2(2) & 16.4(5) \\
%MWA & 200 & 60506.542809(33) & 57(7) & 9(4) \\
%MWA & 200 & 60510.564531(11) & 79(3) & 16(1) \\
%MWA & 200 & 60519.528812(29) & 86(10) & 14(4) \\
%MWA & 200 & 60522.533028(16) & 76(3) & 18(2) \\
%MWA & 200 & 60527.524033(14) & 73(3) & 16(2) \\
%MWA & 200 & 60530.528339(16) & 68(4) & 17(2) \\
%MWA & 200 & 60537.506042(13) & 92(4) & 17(2) \\
%MWA & 200 & 60541.479448(47) & 41(6) & 14(5) \\
%MWA & 200 & 60544.483761(15) & 79(3) & 20(2) \\
%MWA & 200 & 60551.461625(16) & 85(4) & 16(2) \\
%MWA & 185 & 60572.395455(15) & 74(3) & 15(2) \\
%MWA & 185 & 60572.443943(21) & 73(4) & 16(2) \\
%MWA & 185 & 60572.540824(18) & 64(4) & 16(2) \\
%MWA & 185 & 60572.589281(31) & 82(8) & 21(4) \\
%MWA & 200 & 60592.456765(27) & 34(3) & 19(3) \\
%MWA & 200 & 60592.505159(33) & 35(4) & 19(4) \\
%MWA & 200 & 60593.474369(26) & 29(3) & 15(3) \\
%MWA & 200 & 60593.522901(46) & 27(4) & 19(5) \\
%MWA & 200 & 60594.443484(21) & 43(3) & 18(2) \\
%MWA & 200 & 60594.491990(33) & 19(2) & 12(4) \\
%MWA & 200 & 60595.461118(29) & 33(3) & 19(3) \\
%MWA & 200 & 60595.509617(25) & 27(2) & 13(3) \\
%MWA & 200 & 60596.430283(20) & 39(3) & 16(2) \\
%MWA & 200 & 60596.478721(23) & 39(3) & 17(3) \\
%MWA & 200 & 60597.447846(41) & 22(3) & 16(5) \\
%MWA & 200 & 60597.496319(30) & 38(4) & 19(3) \\
%MWA & 200 & 60599.434635(17) & 39(2) & 13(2) \\
%MWA & 200 & 60599.483122(24) & 32(3) & 13(3) \\
%MWA & 200 & 60600.500655(31) & 30(3) & 16(4) \\
%MWA & 200 & 60602.438964(32) & 36(4) & 21(4) \\
%MWA & 200 & 60602.487394(27) & 39(3) & 20(3) \\
%MeerKAT & 813 & 60602.5835733(40) & 1.64(4) & 14.9(4) \\
  %\enddata
%\end{deluxetable*}

@@

\begin{table}
  \centering
  \caption{Timing ephemeris for \src{}}
  \label{tbl:ephemeris}
  \begin{tabular}{lc}
    \hline
    Parameter & Value \\
    \hline
    Period (s) & $4186.3283 \pm 0.0003$ \\
    PEPOCH (MJD) & $59965.03791 \pm 0.00003$ \\
    DM (pc/cm$^{-3}$) & $763 \pm 25$ \\
    $\tau_{\rm sc,1 GHz}$ (s) & ${\sim}0.07$ \\
    \hline
  \end{tabular}
\end{table}

\begin{figure*}
  \centering
  \includegraphics[width=0.98\linewidth]{pulse_details.pdf}
  \caption{Timing residuals (top panel) and other pulse properties derived from the fits of \Eqn~\ref{eqn:emg} to the individual light curves (second and third panels). The peak flux, $S_{\rm peak}$, equivalent to the $A$ parameter in \eqn~\ref{eqn:emg}, is the peak flux of the modelled unscattered pulse. The bottom panel displays $S_{\rm peak,1 GHz} = S_{\rm peak} (\nu/{\rm GHz})^{-\alpha}$, where $\alpha = -2$ has been assumed. Notable features of interest include the relative brightness of the early 2023 detections (leftmost two points), and the relative stability of the pulse fluences (and pulse morphology) of the MWA detections in the time range $60480 \le {\rm MJD} \le 60580$.}
  \label{fig:pulse_details}
\end{figure*}

The variability of the pulse brightness, coupled with the fact that none of our detections were simultaneous at multiple telescopes, prohibit a direct spectral index measurement.
We note, however, that the fitted peak flux densities of the ASKAP and MeerKAT pulses are broadly consistent with the MWA flux densities at nearby epochs if an approximate spectral index of $\alpha = -2.0$ is assumed.
The bottom panel of \Fig~\ref{fig:pulse_details} shows the peak flux densities scaled to 1\,GHz under this assumption, revealing a relatively slow change of the pulses' brightness, not unlike GLEAM-X\,J1627$-$5235 \citep{2022Natur.601..526H}.
The in-band spectral index measurement of $-3.1$ reported for the 2023 ASKAP pulse \citepalias{2024MNRAS.535..909D}, if consistent across the timespan of our observations, implies a turnover or spectral curvature at intermediate frequencies \citep[perhaps comparable with GPM\,1839$-$10][]{2023Natur.619..487H}.

The measured DM of $763 \pm 25\,{\rm pc}\,{\rm cm}^{-3}$ is slightly higher than, but still consistent with, the in-band measurement of $710^{+200}_{-180}\,{\rm pc}\,{\rm cm}^{-3}$ given in \citetalias{2024MNRAS.535..909D}.
Because we have not attempted to simultaneously fit for both DM and scattering timescale, there will remain some small systematic error on this reported DM measurement.
Note, in particular, that the YMW16 and NE2001 models predict a slightly longer scattering time scale than the $70\,$ms that we have assumed throughout this work.
Breaking the degeneracy is possible in principle with a higher S/N average profile than what is achievable with the current data set.

@@

No significant polarised emission was detected in the MWA pulses, as well as the 2023 MeerKAT pulses.
The apparent lack of polarisation in the 2023 MeerKAT data set is likely due to low S/N coupled with the source not being centred in the beam.
Much more careful imaging analysis would be needed to obtain reliable measurements or limits on the polarised components of those pulses.

@@

S.M. would like to thank J. Pritchard and E. Lenc for technical discussions regarding the ASKAP data sets included in this paper.
